Location of Bivalve Farms

### 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
Finished reorganizing data

@@

@@

Now we will map the remaining countries with bivalve farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it. We will gapfill later.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).

5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
 - country, species, n_existing_points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

## Read in ASC data
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

@@

We filter out france and great britain, because those farms are already accounted for in the EMODnet database (which are comprehensive datasets taken from lease data).

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

## save farm location
write.csv(farms_all_fin, here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv"), row.names = FALSE)

@@

Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.

# China

Current data is from ASC, only 11 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_chn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "CHN") %>%
  mutate(data_quality = 2)

write_csv(farms_chn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))

# New Zealand

We currently know the exact location of 2 bivalve farms in New Zealand, however there is much more production that just 2 farms in New Zealand. Although outdated, the FAO report tells us there are 910 total abaolne, mussel, and oyster farms in New Zealand. We will treat this as truth.

 -  Need to add 908 points to existing 2 (a final total of 910 points)

 - http://www.fao.org/fishery/countrysector/naso_newzealand/en

  - “In 2004 there were 645 New Zealand mussel farms occupying a total of 4 747 hectares of water space and producing over 85 000 tonnes of mussels (NZAC, 2005). The majority of these farms were in the Marlborough Sounds at the northern end of the South Island. A smaller proportion of the mussel farms are located in the Coromandel and Hauraki Gulf in the north of the North Island, and a smaller number again at Stewart Island. More recently, permission has been given to develop farming in some larger offshore areas in the Bay of Plenty and Hawkes Bay off the eastern coast of the North Island.”

  - “In 2004 there were 230 oyster farms covering 750 hectares of marine waters mostly in a series of sheltered harbours on the north-eastern coast of the North Island (NZAC, 2005). These farms produced around 3 300 tonnes of oysters.”

  - “A further 35 abalone farms operated over 20 hectares of marine water space producing only 2 tonnes of product in 2004 (NZAC, 2005). Most of these farms were located in the Marlborough Sounds or on Banks Peninsula on the eastern coast of the South Island.”

```{r}
farms_nzl <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "NZL") %>%
  mutate(data_quality = 4)

write.csv(farms_nzl, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_nzl.csv"), row.names = FALSE)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
nz_additional <- data.frame(iso3c = "NZL", type = "bivalve", num_additional_farms = 908, data_quality = 4, total_farms = 910)
write.csv(nz_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_nz.csv"), row.names = FALSE)
```

# South Africa

We currently know the exact location of 2 bivalve farms in South Africa, however there is much more production that just 2 farms. However, governemnt websites and research papers say that there are 4 mussel farms and 21 abalone farms. We will treat this as truth.

 - Need to add 23 points to existing 2 (a final total of 25 points)
 - https://southafrica.co.za/mussel-production.html
   - “According to The Department of Agriculture, Forestry and Fisheries (DAFF), mussel farming in South Africa is conducted entirely in Saldanha Bay, Western Cape, where four mussel farms are operational.”
 - https://core.ac.uk/download/pdf/62634432.pdf
  - We can tell from Figure 1B that there are 21 abalone farms in South Africa

```{r}
farms_zaf <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "ZAF") %>%
  mutate(data_quality = 4)

write.csv(farms_zaf, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_zaf.csv"), row.names = FALSE)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
zaf_additional <- data.frame(iso3c = "ZAF", type = "bivalve", num_additional_farms = 23, data_quality = 4, total_farms = 25)
write.csv(zaf_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_zaf.csv"), row.names = FALSE)
```

# Australia

We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm. However, aquaculture websites say there are 20 abalone farms, 14 oyster farms, and 25 mussel farms in Australia

Need to add 68 points to existing 1 point (for a total of 69 points)

 - Abalone
  - https://www.oceanwatch.org.au/seafood/aquaculture/species/abalone/
  - “There are around 20 farms that produce about 725 tonnes of abalone every year, with production volume increasing by about 25% every year.”
  - 725 tonnes of abalone matches really well to what is reported for abalone in Australia by the FAO.

 - Oysters
  - This states that nearly all oyster license holders are a part of this association:   
  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
  - We will use this as truth: http://www.oysterssa.com.au/south-australian-oyster-growers
  - We will need to place an additional 14 oyster farms in Australia

 - Mussels
  - https://www.oceanwatch.org.au/seafood/aquaculture/species/mussels/
  - “Concentrated in the south of country, there are about 25 mussel farms spread across SA, Tasmania, Victoria, Tasmania and the south coasts of both NSW and WA.”

  - We will place a total of 69 bivalve points in Australia.

```{r}
farms_AUS <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "AUS") %>%
  mutate(data_quality = 4)

write.csv(farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 68, data_quality = 4, total_farms = 69)
write.csv(AUS_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_aus.csv"), row.names = FALSE)
```

# South Korea 
We currently know the exact location of 27 bivalve farms in South Korea, however there is much more production that just 27 farms. However, FAO says there are 5245 shell fish leases in South Korea. WE will place an additional 5218 farms.

Need to add 5218 points to existing 27 (a final total of 5245 points)
 - FAO states there are 5,245 shellfish leases in operation:     
  - http://www.fao.org/fishery/countrysector/naso_korea/en

```{r}
farms_kor <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "KOR") %>%
  mutate(data_quality = 4)

write_csv(farms_kor, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_kor.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
kor_additional <- data.frame(iso3c = "KOR", type = "bivalve", num_additional_farms = 5218, data_quality = 4, total_farms = 5245)
write.csv(kor_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_kor.csv"), row.names = FALSE)
```

# Japan

Current data is from ASC, only 55 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Japan. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_jpn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "JPN") %>%
  mutate(data_quality = 2)

write_csv(farms_jpn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_jpn.csv"))

# Peru

We currently know the exact location of 25 bivalve farms in Peru, however there is much more production that just 25 farms. However, FAO says there are 52 bivalve farms in Peru. We will place an additional 27 farms (for a total of 52 farms).

 - Need to add 27 points to existing 25 (a final total of 52 points)
   - http://www.fao.org/fishery/countrysector/naso_peru/en
   - “It is estimated that Peru has some 14 164 ha apt for the development of marine cultures; of which 86 percent correspond to the region of Ancash (7 228.14ha) and to Ica (5 017.97 ha). Nevertheless, as of December 2003, leased and authorized areas amount to only 8 858 ha. Of this total, 3 033 ha are dedicated to the cultivation of the fan shell.
   - At present, of the 44 referred enterprises, 26 holding 1 662.8 ha are located in the Ancash region; followed by the Ica region, where 18 enterprises occupy 136.8 ha; and the Piura Region has 8 enterprises that develop their activities in 787,6 ha. The majority are large scale operations, with the exception of those located in the Ica region which are relatively small.”

```{r}
farms_per <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "PER") %>%
  mutate(data_quality = 4)

write_csv(farms_per, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_per.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
per_additional <- data.frame(iso3c = "PER", type = "bivalve", num_additional_farms = 27, data_quality = 4, total_farms = 52)
write.csv(per_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_per.csv"), row.names = FALSE)
```

# Mexico
Current data is from ASC, only 1 farm, so definitely not comprehensive, just a drop in the bucket compared to the production of Mexico. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_mex <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "MEX") %>%
  mutate(data_quality = 2)

write_csv(farms_mex, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))

# Jersey
Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are only 7 leases in Jersey.

```{r}
farms_jey <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "JEY") %>%
  mutate(data_quality = 5)

write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_jey.csv"))

# Viet Nam

Current data is from ASC, only 1 farm, so definitely not comprehensive, just a drop in the bucket compared to the production of Viet Nam. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_vnm <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "VNM") %>%
  mutate(data_quality = 2)

write_csv(farms_vnm, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))

# Portugal

We currently know the exact location of 1 bivalve farm in Portugal, however there is much more production that just 1 farm. However, Portuguese government data says there are 30 bivalve farms in Portugal We will place an additional 29 farms (for a total of 30 farms).

Need to add 29 points to existing 1 (a final total of 30 points)

Current data is ASC data which is only a subset of total farms.

 - https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=435690295&PUBLICACOESmodo=2&fbclid=IwAR0-_SHYtw2XGUAXdx71RGer284Vk_u40HYKXyJzeFbpdnsHydKgAfomTvU
  - National Institute of Statistics for Portugal 
  - There is a csv table, "q5_1.csv", which has the number of farms listed by type of system. I will assume that floating marine structures are for bivalves, since [this website](https://rea.apambiente.pt/content/aquaculture-production?language=en) says that the tanks are for **fish production**, and floating structures are for **bivalve molluscs**.

  - Located here "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Portugal/EPesca_2019.xlsx"

 - According to this table, there are 30 total marine floating structures

```{r}
farms_prt <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "PRT") %>%
  mutate(data_quality = 4)

write_csv(farms_prt, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_prt.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
prt_additional <- data.frame(iso3c = "PRT", type = "bivalve", num_additional_farms = 29, data_quality = 4, total_farms = 30)
write.csv(prt_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_prt.csv"), row.names = FALSE)
```

# Chile
This data is comprehensive. No gapfilling needed.

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL") %>%
  mutate(data_quality = 5)

write_csv(farms_chile, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chl.csv"))

@@

## USA

Based on the two datasets below, we have an existing 442 bivalve farms. We need to add 761 points to existing 442 (a final total of 1203 points)

Our current information is taken from many different state level sources, but we are definitely still missing some, as California is not included...

 - However, per FAO 2005, there were 1203 saltwater shellfish farms in the USA
  - http://www.fao.org/fishery/countrysector/naso_usa/en

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 4)

@@

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 4)

farms_usa_total <- rbind(farms_us_ne, farms_us_aqua)

all_farms_sf <- st_as_sf(farms_usa_total, coords = c("lon", "lat"),
                         crs = crs(gadm_latlon), agr = "constant")

@@

write_csv(farms_usa_total, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_usa.csv"))

## Now lets make a df for the additional points we will fill in later

usa_additional <- data.frame(iso3c = "USA", type = "bivalve", num_additional_farms = 761 , data_quality = 4, total_farms = 1203)
write.csv(usa_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_usa.csv"), row.names = FALSE)
```

@@

Sweden:

Current data is from HELCOM, but they state that some data is missing for Sweden (likely a very small amount, given the production). There is not much information on how many farms there might be, so we will gapfill Sweden later. Data quality = 2

Germany:

Need to add 10 points to existing 1 point
 - Current data is from HELCOM, which takes from lease data 
 - Data quality = 4

 - However, the only type farmed in germany is the blue mussel, and this source says there are 11 farms there: 
  - https://onlinelibrary.wiley.com/doi/full/10.1111/raq.12465
  - “The German blue mussel aquaculture takes place at the world heritage and National Park of the Wadden Sea. Therein strict restrictions limit the total number of licenses for harvesting mussel seeds and culture areas (Schlauch 1999). In consequence, the number of enterprises, which are organised in two producer associations, is stable at 11 to ten companies since the 1990s.”

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

## Sweden

farms_swe <- farms_bal %>%
  dplyr::filter(iso3c == "SWE") %>%
  mutate(data_quality = 2)

write_csv(farms_swe, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_swe.csv"))

## Germany

farms_deu <- farms_bal %>%
  dplyr::filter(iso3c == "DEU") %>%
  mutate(data_quality = 4)

write_csv(farms_deu, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_deu.csv"))

deu_additional <- data.frame(iso3c = "DEU", type = "bivalve", num_additional_farms = 10 , data_quality = 4, total_farms = 11)
write.csv(deu_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_deu.csv"), row.names = FALSE)

@@

## HELCOM shellfish mariculture areas - Denmark
This data is comprehensive, data quality = 5

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5)

@@

write.csv(farms_bal_area, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_dnk.csv"), row.names = FALSE)
```

## Canada
All of these data are taken from specific governmental sources. They are comprehensive. Data quality = 5.

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon)))
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5)

write_csv(farms_bc, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_bc_can.csv"))

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5)

write_csv(farms_ns, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_ns_can.csv"))

@@

##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece, UK, France

Almost all of this data is comprehensive. The only one that is not is the netherlands. We will note that and gapfill netherlands later on.

https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
https://www.emodnet-humanactivities.eu/view-data.php

@@

Netherlands
 - Need to add 76 points to existing 6 (a final total of 82 points)
 - Current data is from EMODnet and is NOT comprehensive. Only 6 farms locations.
  - http://www.fao.org/fishery/countrysector/naso_netherlands/en
  - “The shellfish sub-sector is the older and economically more significant of the two and consists of 50 companies growing blue mussels (Mytilus edulis) and 32 companies growing oysters (Ostrea edulis and Crassostrea gigas).”

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "France" ~ "FRA",
    COUNTRY == "United Kingdom" ~ "GBR"
  )) %>%
  dplyr::select(-COUNTRY)

farms_eu_no_nld <- farms_eu_final %>%
  filter(iso3c != "NLD") %>%
  mutate(data_quality = 5)

write_csv(farms_eu_no_nld, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_GBR_FRA_IRL_BGR_NOR_ITA_GRC.csv"))

farms_nld <- farms_eu_final %>%
  filter(iso3c == "NLD") %>%
  mutate(data_quality = 4)

write_csv(farms_nld, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_NLD.csv"))

nld_additional <- data.frame(iso3c = "NLD", type = "bivalve", num_additional_farms = 76 , data_quality = 4, total_farms = 82)
write.csv(nld_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_nld.csv"), row.names = FALSE)

@@

## Spain

@@

 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. If we could download tha exact locations, this would be ideal. However, since we can't, we will gapfill locations instead. See archive for how we previously attempted.

Spain bivalves will be treated as if there is no available information, data quality = 1.

```{r}
# Write a file for russia to indicate it has no information and will need to be fully gapfilled
esp_gf <- data.frame(iso3c = "ESP", type = "bivalve", num_additional_farms = NA, data_quality = 1)
write_csv(esp_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_esp.csv"))
```

## Guernsey 
 - https://www.gov.gg/fishing#:~:text=Sea%20Fisheries%20is%20responsible%20for,one%20licensed%20site%20on%20Herm.
 - Sea Fisheries is responsible for the licensing of all shellfish farms within the Bailiwick. There are a total of seven licensed aquaculture sites distributed around Guernsey's west and north coasts, as well as one licensed site on Herm. There is also an oyster farm located in a disused quarry in the north of the island.
 - Allocate 7 farms into the most suitable locations in Guernsey (this is done later, along with the rest of the gapfilling.)
 - For now we will flag this so that we can gapfill later.

>>>>

coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")

@@

## explore
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

@@

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

We filter out france and great britain, because those farms are already accounted for in the EMODnet database.

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

## save farm location
write.csv(farms_all_fin, here("marine/bivalve/bivalve_farms/data/bivalve_sites/ASC_bivalve_farm_lat_lon.csv"), row.names = FALSE)

@@

Now we will map the remaining countries with bivalve farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of bivalve farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia).

# Chile

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_chile, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_chl.csv"))

@@

## USA 
This has a lot of maps, but almost all don't allow downloads: https://coastalscience.noaa.gov/research/marine-spatial-ecology/coastal-aquaculture-planning-portal-capp/?tx_category=shellfish-algae-planning-and-siting

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5.0) %>%
  mutate(action_needed = "Land mask")

@@

write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ne_usa.csv"))

@@

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

all_farms_sf <- st_as_sf(farms_us_aqua, coords = c("lon", "lat"),
                         crs = crs(gadm_latlon), agr = "constant")

@@

write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_wa_ri_usa.csv"))

@@

@@

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write.csv(farms_bal, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_swe_deu.csv"), row.names = FALSE)

@@

## HELCOM shellfish mariculture areas - Denmark

@@

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

write.csv(farms_bal_area, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_dnk.csv"), row.names = FALSE)
```

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon)))
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_bc, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_bc_can.csv"))

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_ns, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ns_can.csv"))

@@

##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece, UK, France
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
https://www.emodnet-humanactivities.eu/view-data.php

@@

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "France" ~ "FRA",
    COUNTRY == "United Kingdom" ~ "GBR"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_eu_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_GBR_FRA_IRL_BGR_NOR_NLD_ITA_GRC.csv"))

@@

## Spain
TODO: Figure out how to download exact locations

@@

 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

How to download: 
 - Make sure you only have the basemap and the "Instalaciones" layers selected.
 - Click on the filter tab and filter for "Marina" aquaculture, and for these shellfish species: 
 Abalón japonés, Almeja babosa, Almeja fina, Almeja japonesa, Almejas nep (Ruditapes spp), Almejas nep (Veneridae), Berberecho, Berberecho verde, Bivalvos, Bígaro, Coquina, Escupiña grabada, Lapa, Navaja recta, Navaja, Oreja de mar, Ostión u ostra japonesa, Ostra u ostra plana, Ostras u ostras planas, Vieira, Volandeira, Zamburiña
 - Download the data and save as a csv.

General location to place points:
 - Alicante: 38.345509445679276, -0.48793746088812184
 - Almeria: 36.83403538312481, -2.46312530015449
 - Asturias: 43.6586646127094, -5.838989914402157
 - Baleares: 39.578993240236755, 2.6312097506887446
 - Cadiz: 36.55518316813145, -6.2759664948571094
 - Cantabria: 43.488143305644364, -3.808940707432179
 - Castellon: 39.98227981322492, 0.025845987383098443
 - Gerona: 41.893397069777485, 3.1931418366760647
 - Granada: 36.69547948740147, -3.403621978170133
 - La Coruna: 43.36941893593161, -8.412121809979775
 - Las Palmas: 28.17841973419213, -15.411897095500123
 - Lugo: Inland, Don't include
 - Malaga: 36.705816371679525, -4.422146790963811
 - Murcia: Inland, don't include
 - Pontevedra: 42.42511968211785, -8.658739084602496
 - Sevilla: Inland, don't include
 - Santa Cruz de Tenerife: 28.464013540472575, -16.25186419732133
 - Tarragona: 41.109958666992036, 1.2538616546744752
 - Valencia: 39.47564987283762, -0.3208672158378773
 - Vizcaya: 43.436972390962005, -2.9200783381913014

Source: 
Acuivisor, 2019. Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/

```{r}
## Read in dataset of company names:
spain_shellfish <- read_csv(here("marine/bivalve/bivalve_farms/data/spain_shellfish_aquaculture.csv"))

head(unique(spain_shellfish$Empresa))

communitiy <- data.frame(companies = unique(spain_shellfish$Provincia))

## there are 21 different cities where shellfish is farmed.

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014),
                        subregion = c("Alicante", "Almeria", "Asturias", "Baleares", "Cadiz", "Cantabria", "Castellon", "Gerona", "Granada", "La Coruna", "Las Palmas", "Malaga", "Pontevedra", "Santa Cruz de Tenerife", "Tarragona", "Valencia", "Vizcaya")) %>%
  mutate(iso3c = "ESP") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_esp, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_esp.csv"))

## visualize it 
farms_esp <-  st_as_sf(farms_esp, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_esp)
